Dominance Regions for Rank Two Cluster Algebras

### 2022-05-02 dominance_regions.tex
Intro edit

  A number of bases for rank two cluster algebras with various defining properties have been constructed.
  A natural starting basis is the so-called \emph{greedy basis} in which all $\rho_{\alpha_0,\alpha_1}$ are non-negative and these coefficients are chosen to be minimal.
  It is known that this choice coincides with the theta basis \cite{GHKK, CGMMRSW}.
  The \emph{standard monomial bases} of $\cA(b,c)$ come from natural identifications of $\cA(b,c)$ with the subalgebras of $\ZZ[x_0^{\pm1},x_1^{\pm1}]$ generated by $x_{k-1}$, $x_k$, $x_{k+1}$, and $x_{k+2}$ for $k\in\ZZ$.
  However, these bases depend on $k$ and the triangular basis is defined by a triangular transition with the stipulation that the basis does not depend on the choice of starting cluster.
  It would be useful to explicitly (or combinatorially) compute the transitions between these and other known bases.
  However, explicit calculations reveal that the $\bfg$-vectors actually appearing in these transitions are far smaller than the entire dominance polygon.

>>>>

  A number of bases for rank two cluster algebras with various defining properties have been constructed.
  A natural starting basis is the so-called \emph{greedy basis} in which all $\rho_{\alpha_0,\alpha_1}$ are non-negative and these coefficients are chosen to be minimal.
  It is known that this choice coincides with the theta basis \cite{GHKK, CGMMRSW}.
  The \emph{standard monomial bases} of $\cA(b,c)$ come from natural identifications of $\cA(b,c)$ with the subalgebras of $\ZZ[x_0^{\pm1},x_1^{\pm1}]$ generated by $x_{k-1}$, $x_k$, $x_{k+1}$, and $x_{k+2}$ for $k\in\ZZ$.
  However, these bases are not mutation invariant.
  The \emph{triangular basis} is defined by a triangular transition from the standard monomial basis.
  The \emph{generic basis} is defined from the categorification of $\cA(b,c)$ using generic representations of an associated quiver.
  It would be useful to explicitly (or combinatorially) compute the transitions between these known bases.
  Interestingly, explicit calculations reveal that the $\bfg$-vectors actually appearing in these transitions are far smaller than the entire dominance polygon.
